\documentclass[../paper.tex]{subfiles}
\usepackage{nmbib}

% Document
\begin{document}
    % i = introduction, c = code references, s = stack overflow, 
    % d = data references or datasets, v = video references, p = paper references, 
    % o = other references, l = library references
    \begin{thebibliography}{00}
        \bibitem{i0} Deafness and hearing loss, World Health Organization, 2021.
        [Online].
        Available: \url{https://www.who.int/news-room/fact-sheets/detail/deafness-and-hearing-loss\#\~:\text=Over\%205\%25\%20of\%20the\%20world\%27s,will\%20have\%20disabling\%20hearing\%20loss.}
        \bibitem{c0}A. Singh, ``Building a Hand Tracking System using OpenCV'' Analytics Vidhya, 2021.
        [Online].
        Available: \url{https://www.analyticsvidhya.com/blog/2021/07/building-a-hand-tracking-system-using-opencv/}
        \bibitem{c1} S. Som, ``Image Classification: American Sign Language using PyTorch'' Medium, 2021.
        [Online].
        Available: \url{https://medium.com/@sachinsom507/image-classification-american-sign-language-using-pytorch-7bef9d7e8a25}
        \bibitem{c2} S. Som, ``Sign Language Recognition with Advanced Computer Vision'' Towards Data Science, 2021.
        [Online].
        Available: \url{https://towardsdatascience.com/sign-language-recognition-with-advanced-computer-vision-7b74f20f3442}
        \bibitem{c3} Y. Bing, ``CNN Facial Landmark'' GitHub, 2021.
        [Online].
        Available: \url{https://github.com/yinguobing/cnn-facial-landmark}
        \bibitem{s0} How can I get the return value of a function passed to multiprocessing.Process?,
        Stack Overflow, 2012.
        [Online].
        Available:
        \url{https://stackoverflow.com/questions/10415028/how-can-i-get-the-return-value-of-a-function-passed-to-multiprocessing-process}
        \bibitem{v0} Real Time Sign Language Detection with Tensorflow Object Detection and Python | Deep Learning SSD
        [Online]
        Available: \url{https://www.youtube.com/watch?v=pDXdlXlaCco}
        \bibitem{v2}Sign language detection with Python and Scikit Learn | Landmark detection | Computer vision tutorial
        [Online]
        Available: \url{https://www.youtube.com/watch?v=MJCSjXepaAM}
        \bibitem{p0} J. Pu, et al., ``Sign language recognition using 3D convolutional neural networks'' Nature Communications, 2021.
        [Online].
        Available: \url{https://www.nature.com/articles/s41467-021-25637-w}
        \bibitem{p1} S. K. Singh, et al., ``Sign language recognition using deep learning: A review'' Scientific Reports, 2023.
        [Online].
        Available: \url{https://www.nature.com/articles/s41598-023-43852-x#:~:text=In%20recent%20years%2C%20utilizing%20deep,recognition%20in%20the%20data%20image.}
        \bibitem{p2} C. Kent, ``Writing & Training a Vision Transformer for ASL Letters'' Medium, 2021.
        [Online].
        Available: \url{https://medium.com/@crsnkntn/writing-training-a-vision-transformer-for-asl-letters-d870c4d3aeb7}
        \bibitem{d0} ``Sign Language and Static Gesture Recognition using Sklearn'' GitHub, 2021.
        [Online].
        Available: \url{https://github.com/mon95/Sign-Language-and-Static-gesture-recognition-using-sklearn/blob/master/Dataset.zip}
        \bibitem{d1} ``Sign Language Recognition using CNN'' GitHub, 2021.
        [Online].
        Available: \url{https://github.com/gchilingaryan/Sign-Language}
        \bibitem{o0} ``MNIST database'' Wikipedia, 2021.
        [Online].
        Available: \url{https://en.wikipedia.org/wiki/MNIST_database#:~:text=The%20MNIST%20database%20(Modified%20National,the%20field%20of%20machine%20learning.}
        \bibitem{o1} ``Convolutional Neural Networks'' Wikipedia, 2021.
        [Online].
        Available: \url{https://en.wikipedia.org/wiki/Convolutional_neural_network}
        \bibitem{o3} ``Convolutional Neural Networks'' Towards Data Science, 2021.
        [Online].
        Available: \url{https://towardsdatascience.com/convolutional-neural-networks-cnns-and-layer-types-9bbd0a05e1a8}
        \bibitem{o4} ``Convolutional Layer'' Science Direct, 2021.
        [Online].
        Available: \url{https://www.sciencedirect.com/topics/engineering/convolutional-layer#:~:text=A%20convolutional%20layer%20is%20the,and%20creates%20an%20activation%20map.}
        \bibitem{o5} ``Convolutional Layer'' Databricks, 2021.
        [Online].
        Available: \url{https://www.databricks.com/glossary/convolutional-layer}
        \bibitem{o6} ``Non Linearity (Activation) layers'' TUM, 2021.
        [Online].
        Available: \url{https://collab.dvb.bayern/display/TUMlfdv/Layers+of+a+Convolutional+Neural+Network#:~:text=A%20non%2Dlinearity%20layer%20in,activation%20map%20as%20its%20output.}
        \bibitem{o7} ``Pooling layers'' Dremio, 2021.
        [Online].
        Available: \url{https://www.dremio.com/wiki/pooling-layers/#:~:text=What%20is%20Pooling%20Layers%3F,retaining%20the%20most%20important%20information.}
        \bibitem{o8} ``Fully connected layers'' Built In, 2021.
        [Online].
        Available: \url{https://builtin.com/machine-learning/fully-connected-layer}
        \bibitem{o9} ``Dropout layers'' Keras, 2021.
        [Online].
        Available: \url{https://keras.io/api/layers/regularization_layers/dropout/#:~:text=Dropout%20class&text=The%20Dropout%20layer%20randomly%20sets,over%20all%20inputs%20is%20unchanged.}
        \bibitem{o10} ``Flatten layers'' GeeksforGeeks, 2021.
        [Online].
        Available: \url{https://www.geeksforgeeks.org/what-is-a-neural-network-flatten-layer/}
        \bibitem{o11} ``Softmax layers'' Machine Learning Mastery, 2021.
        [Online].
        Available: \url{https://machinelearningmastery.com/softmax-activation-function-with-python/}
        \bibitem{o12} ``Softmax layers'' Quora, 2021.
        [Online].
        Available: \url{https://www.quora.com/What-is-Softmax-in-CNN}
        \bibitem{o13} ``Training'' DataCamp, 2021.
        [Online].
        Available: \url{https://campus.datacamp.com/courses/introduction-to-deep-learning-with-pytorch/training-our-first-neural-network-with-pytorch?ex=1#:~:text=The%20purpose%20of%20the%20forward,training%20and%20generating%20new%20predictions.}
        \bibitem{o14} ``Training'' Neptune.ai, 2021.
        [Online].
        Available: \url{https://neptune.ai/blog/backpropagation-algorithm-in-neural-networks-guide#:~:text=In%20the%20backward%20pass%2C%20the,backward%20propagation%2C%20or%20simple%20backpropagation.}
        \bibitem{o15} ``Early stopping'' Educative, 2021.
        [Online].
        Available: \url{https://www.educative.io/answers/what-is-early-stopping#:~:text=Early%20stopping%20is%20a%20technique,validation%20error%20starts%20to%20increase.}
        \bibitem{o16} ``Neural Network Hyperparameters'' Analytics Vidhya, 2021.
        [Online].
        Available: \url{https://www.analyticsvidhya.com/blog/2021/05/tuning-the-hyperparameters-and-layers-of-neural-network-deep-learning/#:~:text=Conclusion-,Neural%20Network%20Hyperparameters%20(Deep%20Learning),it%20adjusts%20its%20internal%20values.}
        \bibitem{o17} ``Batch normalization layers'' Medium, 2021.
        [Online].
        Available: \url{https://medium.com/@francescofranco_39234/batch-normalization-with-pytorch-20cdc205377f}
        \bibitem{l0} ``OpenCV'' OpenCV, 2021.
        [Online].
        Available: \url{https://opencv.org/}
        \bibitem{l1} ``PyTorch'' PyTorch, 2021.
        [Online].
        Available: \url{https://pytorch.org/}
        \bibitem{l2} ``MediaPipe'' MediaPipe, 2021.
        [Online].
        Available: \url{https://mediapipe.dev/}
    \end{thebibliography}

\end{document}
